---
title: "AS3-2: 股市動態"
author: "第 13 組"
date: "`r Sys.time()`"
output:
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE}
# 這些程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr)
```
<hr>

**股票動態**important

股票市場是買賣雙方交易公司股票的地方，也是個人和公司投資的最受歡迎的方式之一。現在估計世界股票市場規模達到數兆。紐約證券交易所位於紐約市，是世界上最大的股票市場。 紐約證券交易所約有2,800家上市公司。在這個問題上，我們將看看其中五家公司的每月股價：IB、通用電氣（GE）、寶潔、可口可樂和波音。此問題中使用的數據來自Infochimps。

使用`read.csv()`下載並讀取以下文件：

+ `data/IBMStock.csv`
+ `data/GEStock.csv`
+ `data/ProcterGambleStock.csv`
+ `data/CocaColaStock.csv`
+ `data/BoeingStock.csv` 

分別存入資料框`IBM`、`GE`、`ProcterGamble`、`CocaCola`和`Boeing`，
每個資料框都有兩個變量，描述如下：

+ `Date`：日期
+ `StockPrice`：給定月份公司的平均股價

在這個案例，我們將看看這些公司的股票動態如何隨著時間的推移而發生變化。

<br><hr>

###  Section-1 Summary Statistics

__§ 1.1__ Our five datasets all have the same number of observations. How many observations are there in each data set?
```{r}
#讀檔
IBM=read.csv("/Users/wenxuanlee/Desktop/R files/tony/unit03/data/IBMStock.csv")
GE=read.csv("/Users/wenxuanlee/Desktop/R files/tony/unit03/data/GEStock.csv")
PG=read.csv("/Users/wenxuanlee/Desktop/R files/tony/unit03/data/ProcterGambleStock.csv")
COKE=read.csv("/Users/wenxuanlee/Desktop/R files/tony/unit03/data/CocaColaStock.csv")
BOE=read.csv("/Users/wenxuanlee/Desktop/R files/tony/unit03/data/BoeingStock.csv")
#480
nrow(IBM)
nrow(GE)
nrow(PG)
nrow(COKE)
nrow(BOE)
```


__§ 1.2__ What is the earliest year in our datasets?
```{r}
#字串換日期
IBM$Date=as.Date(IBM$Date,"%m/%d/%y")
GE$Date=as.Date(GE$Date,"%m/%d/%y")
PG$Date=as.Date(PG$Date,"%m/%d/%y")
COKE$Date=as.Date(COKE$Date,"%m/%d/%y")
BOE$Date=as.Date(BOE$Date,"%m/%d/%y")
#1970
sort(BOE$Date)
```

__§ 1.3__ What is the latest year in our datasets?
```{r}
#2009
sort(BOE$Date,decreasing =TRUE)
```

__§ 1.4__ What is the mean stock price of IBM over this time period?
```{r}
#144.4
mean(IBM$StockPrice)
```

__§ 1.5__ What is the minimum stock price of General Electric (GE) over this time period?
```{r}
#9.294
min(GE$StockPrice)
#method2
which.min(GE$StockPrice)
GE$StockPrice[471]
```

__§ 1.6__ What is the maximum stock price of Coca-Cola over this time period?
```{r}
#146.6
max(COKE$StockPrice)
```

__§ 1.7__ What is the median stock price of Boeing over this time period?
```{r}
#44.88
median(BOE$StockPrice)
```

__§ 1.8__ What is the standard deviation of the stock price of Procter & Gamble over this time period?
```{r}
#18.19
sd(PG$StockPrice)
```

<br><hr>

###  Section-2 Visualizing Stock Dynamics

__§ 2.1__ Around what year did Coca-Cola has its highest stock price in this time period? Around what year did Coca-Cola has its lowest stock price in this time period?
```{r}
#1980
plot(COKE$Date,COKE$StockPrice,type = "l")
#1973-01-01
COKE$Date[which.max(COKE$StockPrice)]
#1980-01-03
COKE$Date[which.min(COKE$StockPrice)]
```


__§ 2.2__ In March of 2000, the technology bubble burst, and a stock market crash occurred. According to this plot, which company's stock dropped more?
```{r}
#GE
plot(GE$Date,GE$StockPrice,type="l",ylim = c(0,210))
lines(IBM$Date,IBM$StockPrice,col="red")
lines(BOE$Date,BOE$StockPrice,col="blue")
lines(PG$Date,PG$StockPrice,col="green")
lines(COKE$Date,COKE$StockPrice,col="purple")
abline(v=as.Date(c("2000-01-01")),lwd=2)

```

__§ 2.3__ (a) Around 1983, the stock for one of these companies (Coca-Cola or Procter and Gamble) was going up, while the other was going down. Which one was going up? 
```{r}
#Coca-Cola
plot(COKE$Date,COKE$StockPrice,type="l",col="red",ylim = c(0,210))
lines(PG$Date, PG$StockPrice,col="blue")
abline(v=as.Date(c("1983-01-01")),lwd=2)
```

(b) In the time period shown in the plot, which stock generally has lower values?
```{r}
#Boeing
plot(GE$Date,GE$StockPrice,type="l",ylim = c(0,210))
lines(IBM$Date,IBM$StockPrice,col="red")
lines(BOE$Date,BOE$StockPrice,col="blue")
lines(PG$Date,PG$StockPrice,col="green")
lines(COKE$Date,COKE$StockPrice,col="purple")
abline(h=mean(GE$StockPrice),col="yellow")
abline(h=mean(IBM$StockPrice),col="pink")
abline(h=mean(BOE$StockPrice),col="orange")
abline(h=mean(PG$StockPrice),col="brown")
abline(h=mean(COKE$StockPrice),col="navy")
```


<br><hr>

###  Section-3 Visualizing Stock Dynamics 1995-2005

__§ 3.1__ Which stock fell the most right after the technology bubble burst in March 2000?
```{r}
#GE
plot(GE$Date[301:432],GE$StockPrice[301:432],type="l",ylim = c(0,210))
lines(IBM$Date,IBM$StockPrice,lty=3,col="red",lwd=2)
lines(BOE$Date,BOE$StockPrice,lty=4,col="blue")
lines(PG$Date,PG$StockPrice,lty=5,col="green",lwd=3)
lines(COKE$Date,COKE$StockPrice,col="purple")
abline(v=as.Date(c("2000-03-01")), lwd=2)
```

__§ 3.2__ Which stock reaches the highest value in the time period 1995-2005?
```{r}
#IBM
plot(GE$Date[301:432],GE$StockPrice[301:432],type="l",ylim = c(0,210))
lines(IBM$Date,IBM$StockPrice,lty=3,col="red",lwd=2)
lines(BOE$Date,BOE$StockPrice,lty=4,col="blue")
lines(PG$Date,PG$StockPrice,lty=5,col="green",lwd=3)
lines(COKE$Date,COKE$StockPrice,col="purple")
abline(v=as.Date(c("2000-03-01")), lwd=2)
```

__§ 3.3__ In October of 1997, there was a global stock market crash that was caused by an economic crisis in Asia. Comparing September 1997 to November 1997, which companies saw a decreasing trend in their stock price? (Select all that apply.)
```{r}
#Boeing
plot(GE$Date[301:432],GE$StockPrice[301:432],type="l",ylim = c(0,210))
lines(IBM$Date,IBM$StockPrice,lty=3,col="red",lwd=2)
lines(BOE$Date,BOE$StockPrice,lty=4,col="blue")
lines(PG$Date,PG$StockPrice,lty=5,col="green",lwd=3)
lines(COKE$Date,COKE$StockPrice,col="purple")
abline(v=as.Date(c("1997-09-01")), lwd=2)
abline(v=as.Date(c("1997-11-01")), lwd=2)
```

__§ 3.4__ In the last two years of this time period (2004 and 2005) which stock seems to be performing the best, in terms of increasing stock price?
```{r}
#Boeing
plot(GE$Date[400:469],GE$StockPrice[400:469],type="l",ylim = c(0,210))
lines(IBM$Date,IBM$StockPrice,lty=3,col="red",lwd=2)
lines(BOE$Date,BOE$StockPrice,lty=4,col="blue")
lines(PG$Date,PG$StockPrice,lty=5,col="green",lwd=3)
lines(COKE$Date,COKE$StockPrice,col="purple")
abline(v=as.Date(c("2004-01-01")), lwd=2)
abline(v=as.Date(c("2005-12-01")), lwd=2)
```


<br><hr>


###  Section-4 Monthly Trends

__§ 4.1__ For IBM, compare the monthly averages to the overall average stock price. In which months has IBM historically had a higher stock price (on average)? Select all that apply.
```{r}
#Jan,Feb,Mar,Apr,May
IBM$month=months(IBM$Date)
mean(IBM$StockPrice)
tapply(IBM$StockPrice,IBM$month,mean)>mean(IBM$StockPrice)
```

__§ 4.2__ General Electric and Coca-Cola both have their highest average stock price in the same month. Which month is this?
```{r}
#Apr
which.max(tapply(GE$StockPrice,months(GE$Date),mean))
which.max(tapply(COKE$StockPrice,months(COKE$Date),mean))
```

__§ 4.3__ For the months of December and January, every company's average stock is higher in one month and lower in the other. In which month are the stock prices lower?
```{r}
#Dec
mean(IBM$StockPrice)
tapply(IBM$StockPrice,months(IBM$Date),mean)
```

<br><br><br>

